Trends of SDR in Thessaloniki

### 2023-11-03 MDPI_submition.Rmd
Commit 2023-11-03 14:14

a) Mean of the measured $\overline{\text{SDR}}_i$ (Eq. \ref{eq:MeanVIP}).
\begin{equation}
`r 1 - CS_ref_rm_VIP_RelLow` \times \overline{\text{SDR}}_{\text{CSref},i} - `r CS_ref_rm_VIP_LowOff`\,Wm^{-2}
< \overline{\text{SDR}}_i <
`r 1 + CS_ref_rm_VIP_RelUpp` \times \overline{\text{SDR}}_{\text{CSref},i} + `r CS_ref_rm_VIP_UppOff`\,Wm^{-2}
\label{eq:MeanVIP}
\end{equation}
<!-- 2. MaxVIP -->
<!-- ### Max value of irradiance during the time period. -->
<!-- The running max measured value $M_{\text{SDR},i} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$, is compared to a similar constructed value from the reference $M_{CSrefi} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq.\ \ref{eq:MaxVIP}). -->
b) Maximum measured value $M_{i}$ (Eq.\ \ref{eq:MaxVIP}).
\begin{equation}
`r MaxVIP_fct` \times M_{\text{CSref},i} - `r MaxVIP_off_low`\,Wm^{-2}
< M_{i} <
`r MaxVIP_fct` \times M_{\text{CSref},i} + `r MaxVIP_off_upp`\,Wm^{-2}
\label{eq:MaxVIP}
\end{equation}
<!-- 3. VIL -->
<!-- ### Variability in irradiance by line length. -->
c) Length $L_i$ of the sequential line segments, connecting the points of the $`r nt`$ SDR values (Eq. \ref{eq:VILeq}).
\begin{equation}
L_i = \sum_{i=1}^{n-1}\sqrt{\left ( \text{SDR}_{i+1} - \text{SDR}_{i}\right )^2 + \left ( t_{i+1} - t_i \right )^2}
\label{eq:VILeq}
\end{equation}
\begin{equation}
`r MinVIL_fct` \times L_{\text{CSref},i} - `r offVIL_dwl` < L_i < `r MaxVIL_fct` \times L_{\text{CSref},i} + `r offVIL_upl`
\label{eq:VILcr}
\end{equation}
where: $t_i$ is the time stamp of each SDR measurement.
<!-- 4. VCT -->
<!-- ### Variance of Changes in the Time series. -->
<!-- Standard deviation of rate of change in irradiance. -->
d) Standard deviation $\sigma_i$ of the slope ($s_i$) between the $`r nt`$ sequential points, normalized by the mean $\overline{\text{SDR}}_i$ (Eq.\ \ref{eq:VCT1}).
<!-- \begin{gather}
\bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i \label{eq:VCT2} \\
\sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2} } {\bar{G_i}} \label{eq:VCT3}
\end{gather} -->
\begin{gather}
  \sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2}} {\overline{\text{SDR}}_i} \label{eq:VCT1} \\
  s_i = \frac{\text{SDR}_{i+1} - \text{SDR}_{i}}{t_{i+1} - t_i},\;\;   \bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i,\;\;\forall i \in \left \{ 1, 2, \ldots, n-1 \right \}\;\;
\end{gather}
For this criterion, $\sigma_i$ should be below a certain threshold (Eq.\ \ref{eq:VCTcr}):
\begin{equation}
  \sigma_i < `r offVCT` \label{eq:VCTcr}
\end{equation}
<!-- 5. VSM -->
<!-- ### Variability in the Shape of the irradiance Measurements. -->
e) Maximum difference $X_i$ between the change in measured irradiance and the change in clear sky irradiance over each measurement interval.
\begin{gather}
  X_i = \max{\left \{ \left | x_i - x_{\text{CSref},i} \right | \right \}} \label{eq:VSM3} \\
  x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
  x_{\text{CSref},i} = \text{SDR}_{\text{CSref},i+1} - \text{SDR}_{\text{CSref},i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2}
\end{gather}
For this criterion, $X_i$ should be below a certain threshold (Eq.\ \ref{eq:VSMcr}):
\begin{equation}
  X_i < `r offVSM` \label{eq:VSMcr}
\end{equation}

<!-- ### Data selection -->
Due to the significant measurement uncertainty when the Sun is near the horizon, we have excluded all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically not visible from the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all one-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a time series of satellite TSI observations.
The TSI data we used are part of the "NOAA Climate Data Record of Total Solar Irradiance" dataset [@Coddington2005]. 
The initial daily values of this dataset were interpolated to match the time step of our measurements. 
In the final dataset
$`r SDR_N_All`$
one-minute measurements, of which, 
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$
were identified as under clear-sky conditions and
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
as under cloud-sky conditions.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->

>>>>

a) Mean of the measured $\overline{\text{SDR}}_i$ (Eq. \ref{eq:MeanVIP}).
\begin{equation}
`r 1 - CS_ref_rm_VIP_RelLow` \times \overline{\text{SDR}}_{\text{CSref},i} - `r CS_ref_rm_VIP_LowOff`\,Wm^{-2}
< \overline{\text{SDR}}_i <
`r 1 + CS_ref_rm_VIP_RelUpp` \times \overline{\text{SDR}}_{\text{CSref},i} + `r CS_ref_rm_VIP_UppOff`\,Wm^{-2}
\label{eq:MeanVIP}
\end{equation}
<!-- 2. MaxVIP -->
<!-- ### Max value of irradiance during the time period. -->
<!-- The running max measured value $M_{\text{SDR},i} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$, is compared to a similar constructed value from the reference $M_{CSrefi} = \max_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq.\ \ref{eq:MaxVIP}). -->
b) Maximum measured value $M_{i}$ (Eq.\ \ref{eq:MaxVIP}).
\begin{equation}
`r MaxVIP_fct` \times M_{\text{CSref},i} - `r MaxVIP_off_low`\,Wm^{-2}
< M_{i} <
`r MaxVIP_fct` \times M_{\text{CSref},i} + `r MaxVIP_off_upp`\,Wm^{-2}
\label{eq:MaxVIP}
\end{equation}
<!-- 3. VIL -->
<!-- ### Variability in irradiance by line length. -->
c) Length $L_i$ of the sequential line segments, connecting the points of the $`r nt`$ SDR values (Eq. \ref{eq:VILeq}).
\begin{equation}
L_i = \sum_{i=1}^{n-1}\sqrt{\left ( \text{SDR}_{i+1} - \text{SDR}_{i}\right )^2 + \left ( t_{i+1} - t_i \right )^2}
\label{eq:VILeq}
\end{equation}
\begin{equation}
`r MinVIL_fct` \times L_{\text{CSref},i} - `r offVIL_dwl` < L_i < `r MaxVIL_fct` \times L_{\text{CSref},i} + `r offVIL_upl`
\label{eq:VILcr}
\end{equation}
where: $t_i$ is the time stamp of each SDR measurement.
<!-- 4. VCT -->
<!-- ### Variance of Changes in the Time series. -->
<!-- Standard deviation of rate of change in irradiance. -->
d) Standard deviation $\sigma_i$ of the slope ($s_i$) between the $`r nt`$ sequential points, normalized by the mean $\overline{\text{SDR}}_i$ (Eq.\ \ref{eq:VCT1}).
<!-- \begin{gather}
\bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i \label{eq:VCT2} \\
\sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2} } {\bar{G_i}} \label{eq:VCT3}
\end{gather} -->
\begin{gather}
  \sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2}} {\overline{\text{SDR}}_i} \label{eq:VCT1} \\
  s_i = \frac{\text{SDR}_{i+1} - \text{SDR}_{i}}{t_{i+1} - t_i},\;\;   \bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i,\;\;\forall i \in \left \{ 1, 2, \ldots, n-1 \right \}\;\;
\end{gather}
For this criterion, $\sigma_i$ should be below a certain threshold (Eq.\ \ref{eq:VCTcr}):
\begin{equation}
  \sigma_i < `r offVCT` \label{eq:VCTcr}
\end{equation}
<!-- 5. VSM -->
<!-- ### Variability in the Shape of the irradiance Measurements. -->
e) Maximum difference $X_i$ between the change in measured irradiance and the change in clear sky irradiance over each measurement interval.
\begin{gather}
  X_i = \max{\left \{ \left | x_i - x_{\text{CSref},i} \right | \right \}} \label{eq:VSM3} \\
  x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
  x_{\text{CSref},i} = \text{SDR}_{\text{CSref},i+1} - \text{SDR}_{\text{CSref},i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2}
\end{gather}
For this criterion, $X_i$ should be below a certain threshold (Eq.\ \ref{eq:VSMcr}):
\begin{equation}
  X_i < `r offVSM`\,Wm^{-2} \label{eq:VSMcr}
\end{equation}

<!-- ### Data selection -->
Due to the significant measurement uncertainty when the Sun is near the horizon, we have excluded all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically not visible from the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all one-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1\,\text{au}$, in order to compensate for the Sun's intensity variability, using a time series of satellite TSI observations.
The TSI data we used are part of the "NOAA Climate Data Record of Total Solar Irradiance" dataset [@Coddington2005]. 
The initial daily values of this dataset were interpolated to match the time step of our measurements. 
In the final dataset
<!-- $`r SDR_N_All`$ -->
$`r signif(100 * SDR_N_Clear / SDR_N_All, 3)`\%$
of the data were identified as under clear-sky conditions and
$`r signif(100 * SDR_N_Cloud / SDR_N_All, 3)`\%$
as under cloud-sky conditions.
<!-- The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @LASP2023 (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).-->

### 2023-11-03 MDPI_submition.tex
Commit 2023-11-03 14:14

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\tightlist
\item
  Mean of the measured \(\overline{\text{SDR}}_i\) (Eq.
  \ref{eq:MeanVIP}). \begin{equation}
  0.91 \times \overline{\text{SDR}}_{\text{CSref},i} - 20\,Wm^{-2}
  < \overline{\text{SDR}}_i <
  1.095 \times \overline{\text{SDR}}_{\text{CSref},i} + 30\,Wm^{-2}
  \label{eq:MeanVIP}
  \end{equation}
\item
  Maximum measured value \(M_{i}\) (Eq.~\ref{eq:MaxVIP}).
  \begin{equation}
  1 \times M_{\text{CSref},i} - 75\,Wm^{-2}
  < M_{i} <
  1 \times M_{\text{CSref},i} + 75\,Wm^{-2}
  \label{eq:MaxVIP}
  \end{equation}
\item
  Length \(L_i\) of the sequential line segments, connecting the points
  of the \(11\) SDR values (Eq. \ref{eq:VILeq}). \begin{equation}
  L_i = \sum_{i=1}^{n-1}\sqrt{\left ( \text{SDR}_{i+1} - \text{SDR}_{i}\right )^2 + \left ( t_{i+1} - t_i \right )^2}
  \label{eq:VILeq}
  \end{equation} \begin{equation}
  1 \times L_{\text{CSref},i} - 5 < L_i < 1.3 \times L_{\text{CSref},i} + 13
  \label{eq:VILcr}
  \end{equation} where: \(t_i\) is the time stamp of each SDR
  measurement.
\item
  Standard deviation \(\sigma_i\) of the slope (\(s_i\)) between the
  \(11\) sequential points, normalized by the mean
  \(\overline{\text{SDR}}_i\) (Eq.~\ref{eq:VCT1}). \begin{gather}
    \sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2}} {\overline{\text{SDR}}_i} \label{eq:VCT1} \\
    s_i = \frac{\text{SDR}_{i+1} - \text{SDR}_{i}}{t_{i+1} - t_i},\;\;   \bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i,\;\;\forall i \in \left \{ 1, 2, \ldots, n-1 \right \}\;\;
  \end{gather} For this criterion, \(\sigma_i\) should be below a
  certain threshold (Eq.~\ref{eq:VCTcr}): \begin{equation}
    \sigma_i < \ensuremath{1.1\times 10^{-4}} \label{eq:VCTcr}
  \end{equation}
\item
  Maximum difference \(X_i\) between the change in measured irradiance
  and the change in clear sky irradiance over each measurement interval.
  \begin{gather}
    X_i = \max{\left \{ \left | x_i - x_{\text{CSref},i} \right | \right \}} \label{eq:VSM3} \\
    x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
    x_{\text{CSref},i} = \text{SDR}_{\text{CSref},i+1} - \text{SDR}_{\text{CSref},i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2}
  \end{gather} For this criterion, \(X_i\) should be below a certain
  threshold (Eq.~\ref{eq:VSMcr}): \begin{equation}
    X_i < 7.5 \label{eq:VSMcr}
  \end{equation}
\end{enumerate}

Due to the significant measurement uncertainty when the Sun is near the
horizon, we have excluded all measurements with SZA greater than
\(85^\circ\). Moreover, due to some obstructions around the site (hills
and buildings), we excluded data with azimuth angle between \(35^\circ\)
and \(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically not visible from the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all one-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1\,\text{au}\), in order to compensate for
the Sun's intensity variability, using a time series of satellite TSI
observations. The TSI data we used are part of the ``NOAA Climate Data
Record of Total Solar Irradiance'' dataset \citep{Coddington2005}. The
initial daily values of this dataset were interpolated to match the time
step of our measurements. In the final dataset \(6589967\) one-minute
measurements, of which, \(84.2\%\) were identified as under clear-sky
conditions and \(15.8\%\) as under cloud-sky conditions.

>>>>

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\tightlist
\item
  Mean of the measured \(\overline{\text{SDR}}_i\) (Eq.
  \ref{eq:MeanVIP}). \begin{equation}
  0.91 \times \overline{\text{SDR}}_{\text{CSref},i} - 20\,Wm^{-2}
  < \overline{\text{SDR}}_i <
  1.095 \times \overline{\text{SDR}}_{\text{CSref},i} + 30\,Wm^{-2}
  \label{eq:MeanVIP}
  \end{equation}
\item
  Maximum measured value \(M_{i}\) (Eq.~\ref{eq:MaxVIP}).
  \begin{equation}
  1 \times M_{\text{CSref},i} - 75\,Wm^{-2}
  < M_{i} <
  1 \times M_{\text{CSref},i} + 75\,Wm^{-2}
  \label{eq:MaxVIP}
  \end{equation}
\item
  Length \(L_i\) of the sequential line segments, connecting the points
  of the \(11\) SDR values (Eq. \ref{eq:VILeq}). \begin{equation}
  L_i = \sum_{i=1}^{n-1}\sqrt{\left ( \text{SDR}_{i+1} - \text{SDR}_{i}\right )^2 + \left ( t_{i+1} - t_i \right )^2}
  \label{eq:VILeq}
  \end{equation} \begin{equation}
  1 \times L_{\text{CSref},i} - 5 < L_i < 1.3 \times L_{\text{CSref},i} + 13
  \label{eq:VILcr}
  \end{equation} where: \(t_i\) is the time stamp of each SDR
  measurement.
\item
  Standard deviation \(\sigma_i\) of the slope (\(s_i\)) between the
  \(11\) sequential points, normalized by the mean
  \(\overline{\text{SDR}}_i\) (Eq.~\ref{eq:VCT1}). \begin{gather}
    \sigma_i = \frac {\sqrt{\frac{1}{n-1} \sum_{i=1}^{n-1} \left( s_i - \bar{s} \right)^2}} {\overline{\text{SDR}}_i} \label{eq:VCT1} \\
    s_i = \frac{\text{SDR}_{i+1} - \text{SDR}_{i}}{t_{i+1} - t_i},\;\;   \bar{s} = \frac{1}{n-1} \sum_{i=1}^{n-1} s_i,\;\;\forall i \in \left \{ 1, 2, \ldots, n-1 \right \}\;\;
  \end{gather} For this criterion, \(\sigma_i\) should be below a
  certain threshold (Eq.~\ref{eq:VCTcr}): \begin{equation}
    \sigma_i < \ensuremath{1.1\times 10^{-4}} \label{eq:VCTcr}
  \end{equation}
\item
  Maximum difference \(X_i\) between the change in measured irradiance
  and the change in clear sky irradiance over each measurement interval.
  \begin{gather}
    X_i = \max{\left \{ \left | x_i - x_{\text{CSref},i} \right | \right \}} \label{eq:VSM3} \\
    x_i = \text{SDR}_{i+1} - \text{SDR}_{i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM1} \\
    x_{\text{CSref},i} = \text{SDR}_{\text{CSref},i+1} - \text{SDR}_{\text{CSref},i} \forall i \in \left \{ 1, 2, \ldots, n-1 \right \} \label{eq:VSM2}
  \end{gather} For this criterion, \(X_i\) should be below a certain
  threshold (Eq.~\ref{eq:VSMcr}): \begin{equation}
    X_i < 7.5\,Wm^{-2} \label{eq:VSMcr}
  \end{equation}
\end{enumerate}

Due to the significant measurement uncertainty when the Sun is near the
horizon, we have excluded all measurements with SZA greater than
\(85^\circ\). Moreover, due to some obstructions around the site (hills
and buildings), we excluded data with azimuth angle between \(35^\circ\)
and \(120^\circ\) with SZA greater than \(80^\circ\). On the latter
instances, Sun is systematically not visible from the instrument's
location. To make the measurements comparable throughout the dataset, we
adjusted all one-minute radiometric values to the mean Sun - Earth
distance. Subsequently, we made all measurements relative to the Total
Solar Irradiance (TSI) at \(1\,\text{au}\), in order to compensate for
the Sun's intensity variability, using a time series of satellite TSI
observations. The TSI data we used are part of the ``NOAA Climate Data
Record of Total Solar Irradiance'' dataset \citep{Coddington2005}. The
initial daily values of this dataset were interpolated to match the time
step of our measurements. In the final dataset \(84.2\%\) of the data
were identified as under clear-sky conditions and \(15.8\%\) as under
cloud-sky conditions.
